Now That's Fresh Water

### 2022-04-03 outputs/paper/paper.Rmd
proofreading done, final commit

Now we study is the interaction between our variables. That is, if a change in one is affecting a change in another, on some outcome. To aid in this process, we define our two yields, or outcomes, as the immunization rate and birth in health facility rate of children. This makes sense as these two variables serve as indicators of the wellbeing of children in the country. Then our 3 predictors are the illiteracy rate, access to water rate, and antenatal care rate.

@@

The first comparison we make is between the percentage of illiterate females and the percentage of vaccinated children. This will tell us the effect education of the mother has on the benefit of their child. The graph below in Figure 5 shows that as illiteracy rate goes up, the rate of vaccination goes down. This seems indicative that educated women are more likely to vaccinate their children.

@@

To facilitate the delivery of the survey, the NFHS team may consider administering it online. When the survey was initially conducted in 1992, nearly the entire population did not have access to any form of internet communication, but now, as of 2019, over 41% of the population is online (@internet). As demonstrated by organizations like Statistics Canada, it’s the least expensive mode, and it can be used to reach a very large number of people (@statcan). The respondent can fill the survey at the moment of his choice. Self-completed (i.e. online) questionnaires are also easier when the survey questions are sensitive, such as some of the topics covered by the NFHS. The downside of this mode is that response rates are lower than for other collection mode and the quality of collected data can suffer (@statcan). Despite the detriments, it is still advisable out of the interest of safety, especially to avoid key areas that were missed because of uncharted terrain and potential threats in various villages.

>>>>

Now we study the interaction between our variables. That is, if a change in one is affecting a change in another, on some outcome. To aid in this process, we define our two yields, or outcomes, as the immunization rate and birth in health facility rate of children. This makes sense as these two variables serve as indicators of the wellbeing of children in the country. Then our 3 predictors are the illiteracy rate, access to water rate, and antenatal care rate.

@@

The first comparison we make is between the percentage of illiterate females and the percentage of immunized children. This will tell us the effect education of the mother has on the benefit of their child. The graph below in Figure 5 shows that as illiteracy rate goes up, the rate of vaccination goes down. This seems indicative that educated women are more likely to vaccinate their children.

@@

To facilitate the delivery of the survey, the NFHS team may consider administering it online. When the survey was initially conducted in 1992, nearly the entire population did not have access to any form of internet communication, but now, as of 2019, over 41% of the population has internet (@internet). As demonstrated by organizations like Statistics Canada, it’s the least expensive mode, and it can be used to reach a very large number of people (@statcan). The respondent can fill the survey at the moment of his choice. Self-completed (i.e. online) questionnaires are also easier when the survey questions are sensitive, such as some of the topics covered by the NFHS. The downside of this mode is that response rates are lower than for other collection mode and the quality of collected data can suffer (@statcan). Despite the detriments, it is still advisable out of the interest of safety, especially to avoid key areas that were missed because of uncharted terrain and potential threats in various villages.
